\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
        {\textbf{2026 SouthEastCon Robotics Competition}}{Sep 2025 -- Present}
        {Group Project}
        \resumeItemListStart
          \resumeItem{Integrated Raspberry Pi 5 into Hardware-in-the-Loop (HIL) system for autonomous robot software development, configuring Docker containers, VSCode remote development, and Cloudflare tunneling to enable collaborative testing environment for 10+ team members.}
          \resumeItem{Testing micro-ROS packages on Raspberry Pi to validate real-time ROS2 communication protocols, ensuring reliable message passing between embedded systems before hardware integration with FPGA and ESP32 microcontrollers.}
          \resumeItem{Designing automated startup scripts for Docker container deployment to streamline robot boot process and reduce setup time during competition testing.}
          \resumeItem{Contributing to PCB design and layout for mini UAV flight controller, focusing on component placement, power distribution, and signal integrity for autonomous navigation systems.}
        \resumeItemListEnd
        
      %\resumeProjectHeading
        %{\textbf{2026 SouthEastCon Robotics Competition}}{Sep 2024 -- Present}
        %{Group Project}
        %\resumeItemListStart
          %\resumeItem{Configured Raspberry Pi 5 development environment by flashing Raspberry Pi Desktop OS, setting up Git, Docker Desktop, VSCode Dev Containers extension, and Cloudflare tunneling to access team's Gitea repository for autonomous robot software development.}
          %\resumeItem{Resolved Gazebo simulation compatibility issues on ARM architecture by enabling software rendering through environment variables and modifying initialization scripts to uncomment Linux-specific commands, enabling simulation testing on Raspberry Pi hardware.}
          %\resumeItem{Testing micro-ROS packages and designing automated startup scripts for Docker container deployment to streamline robot development and competition preparation.}
          %\resumeItem{Contributing to PCB design and layout for mini UAV flight controller, focusing on component placement, power distribution, and signal integrity for autonomous navigation systems.}
        %\resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{KnightCore -- FPGA Integration -- 2025 AMD Hardware Competition}}{Apr 2025 -- Aug 2025}
        {Group Project}
        \resumeItemListStart
          \resumeItem{Solely responsible for integrating custom GPU hardware module onto Red Pitaya Zynq FPGA platform using Vivado block design, connecting Zynq processor, AXI interconnect, BRAM controller/memory, configuring address spaces in the housekeeping region, and generating bitstreams, enabling team to focus exclusively on hardware design.}
          \resumeItem{Debugged memory-mapped I/O communication issues between ARM processor and FPGA programmable logic, identifying and correcting address mapping errors in shared memory regions to enable successful hardware integration.}
          \resumeItem{Developed and executed shell script and Python-based validation tests on Red Pitaya to verify register read/write operations and confirm successful processor-to-FPGA communication through memory-mapped interfaces.}
        \resumeItemListEnd
        
      %\resumeProjectHeading
        %{\textbf{KnightCore -- FPGA Integration -- 2025 AMD Hardware Competition}}{Apr 2025 -- Aug 2025}
        %{Group Project}
        %\resumeItemListStart
          %\resumeItem{Integrated custom GPU hardware module onto Red Pitaya Zynq FPGA platform using Vivado block design, connecting Zynq processor, AXI interconnect, BRAM controller/memory, configuring address spaces in housekeeping region, and generating bitstreams.}
          %\resumeItem{Debugged memory-mapped I/O communication issues between ARM processor and FPGA programmable logic, identifying and correcting address mapping errors in shared memory regions to enable successful hardware integration.}
          %\resumeItem{Developed and executed shell script and Python-based validation tests on Red Pitaya to verify register read/write operations and confirm successful processor-to-FPGA communication through memory-mapped interfaces.}
        %\resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{RISC-V CPU}}{Jul 2025 -- Present}
        {Solo Project}
        \resumeItemListStart
          \resumeItem{Designing a 32-bit single-cycle RISC-V processor from scratch on Red Pitaya FPGA, implementing the RV32I base instruction set with ALU operations, load/store instructions, and control logic using Verilog and SystemVerilog.}
          \resumeItem{Architecting datapath components including register file, arithmetic logic unit, instruction decoder, and control unit to execute instructions through fetch-decode-execute cycle.}
          \resumeItem{Developing verification infrastructure using UVM (Universal Verification Methodology) and functional verification techniques to validate instruction execution, register file operations, and memory interface functionality against RISC-V specification requirements.}
        \resumeItemListEnd
        
      %\resumeProjectHeading
        %{\textbf{RISC-V CPU}}{Jul 2025 -- Present}
        %{Solo Project}
        %\resumeItemListStart
          %\resumeItem{Designing a 32-bit single-cycle RISC-V processor from scratch on Red Pitaya FPGA, implementing the RV32I base instruction set with ALU operations, load/store instructions, and control logic using Verilog and SystemVerilog.}
          %\resumeItem{Architecting datapath components including register file, arithmetic logic unit, instruction decoder, and control unit to execute instructions through fetch-decode-execute cycle.}
          %\resumeItem{Developing testbenches to validate instruction execution, register file operations, and memory interface functionality against RISC-V specification requirements.}
        %\resumeItemListEnd

      \resumeProjectHeading
        {\textbf{4 Cluster PC Home Lab}}{Sep 2025 -- Present}
        {Solo Project}
        \resumeItemListStart
          \resumeItem{Designing and deploying distributed computing infrastructure using 4 Mini PCs configured in a Proxmox High Availability cluster with ZFS replication for self-hosted services, network experimentation, and cybersecurity training.}
          \resumeItem{Implementing containerized services using Docker and Kubernetes for application deployment, alongside network security tools including Wireshark, Security Onion, and Kali Linux for penetration testing and threat detection.}
          \resumeItem{Configuring network segmentation with VLAN architecture, OPNsense firewall rules, and VPN tunneling through WireGuard to isolate services and implement enterprise-grade security best practices.}
        \resumeItemListEnd

      %\resumeProjectHeading
        %{\textbf{IEEE Resume Database}}{Sep 2025 -- Present}
        %{Group Project}
        %\resumeItemListStart
          %\resumeItem{Developed HTML input form structure for IEEE UCF chapter resume database, creating form fields for member information including name, college, education history, work experience, projects, skills, and affiliations.}
          %\resumeItem{Implementing dynamic array input functionality for links and projects sections, enabling members to add multiple entries through interactive form controls.}
          %\resumeItem{Building front-end display components using React to present stored resume data with text fields instead of input forms for viewing member profiles.}
        %resumeItemListEnd

    \resumeSubHeadingListEnd
